\textsf{Are large language models superhuman chemists?}

### 2024-08-21 src/tex/ms.tex
feat: shorten abstract

\clearpage
\begin{abstract}
    Large language models (LLMs) have gained widespread interest due to their ability to process human language and perform tasks on which they have not been explicitly trained. 
    This is relevant for the chemical sciences, which face the problem of small and diverse datasets that are frequently in the form of text.
    LLMs have shown promise in addressing these issues and are increasingly being harnessed to predict chemical properties, optimize reactions, and even design and conduct experiments autonomously.

    However, we still have only a very limited systematic understanding of the chemical reasoning capabilities of LLMs, which would be required to improve models and mitigate potential harms. 
    Here, we introduce \enquote{\chembench,} an automated framework designed to rigorously evaluate the chemical knowledge and reasoning abilities of state-of-the-art LLMs against the expertise of human chemists.

    We curated more than 7,000 question-answer pairs for a wide array of subfields of the chemical sciences, evaluated leading open and closed-source LLMs, and found that the best models outperformed the best human chemists in our study on average. 
    The models, however, struggle with some chemical reasoning tasks that are easy for human experts and provide overconfident, misleading predictions, such as about chemicals' safety profiles.

    These findings underscore the dual reality that, although LLMs demonstrate remarkable proficiency in chemical tasks, further research is critical to enhancing their safety and utility in chemical sciences.
    Our findings also indicate a need for adaptations to chemistry curricula and highlight the importance of continuing to develop evaluation frameworks to improve safe and useful LLMs.
\end{abstract}

>>>>

\clearpage
\begin{abstract}
    Large language models (LLMs) have gained widespread interest due to their ability to process human language. 
    Also, LLMs have shown promise in addressing the limited data problem in chemistry and are increasingly being harnessed to improve and extend existing workflows.

    However, we possess only a limited systematic understanding of the reasoning capabilities of LLMs, which would be required to improve models and mitigate potential harms. 
    Here, we introduce \enquote{\chembench,} an automated framework for evaluating the chemical knowledge and reasoning abilities of state-of-the-art LLMs against the expertise of chemists.

    We curated more than 7,500 question-answer pairs, evaluated leading open and closed-source LLMs, and found that, on average, the best models outperformed the chemists. 
    The models, however, struggle with some chemical reasoning tasks that are easy for the human experts and provide overconfident, misleading predictions, such as about chemicals' safety profiles. 
    Although LLMs demonstrate remarkable proficiency in chemical tasks, further research is critical to enhancing their safety and utility in chemical sciences.
\end{abstract}
